---
title: "Syllabus"
---

```{r setup, message=FALSE, warning=FALSE, include=FALSE}
library(dplyr)
library(tibble)
library(pander)
```

::: {.grid .course-details .course-details-smaller}

::: {.g-col-6}
### Instructor

- {{< fa user >}} &nbsp; [{{< var instructor.name >}}]({{< var instructor.url >}})
- {{< fa university >}} &nbsp; {{< var instructor.office >}}
- {{< fa envelope >}} &nbsp; <a href="mailto:{{< var instructor.email >}}">{{< var instructor.email >}}</a>
- {{< fa brands twitter >}} &nbsp; [{{< var instructor.twitter >}}](https://www.twitter.com/{{< var instructor.twitter >}})
- {{< fa calendar-check >}} &nbsp; [Schedule an appointment]({{< var instructor.appointment_url >}})
:::

::: {.g-col-6}
### Course details

- {{< fa calendar >}} &nbsp; {{< var course.days >}}
- {{< fa calendar-alt >}} &nbsp; {{< var course.dates >}}
- {{< fa clock >}} &nbsp; {{< var course.time >}}
- {{< fa location-dot >}} &nbsp; {{< var course.location >}}
:::

:::


## Course objectives

The nonprofit sector is a core part of the US economy, and nonprofit organizations play a vibrant role in American civic life. Nonprofits are far more important than you might realize! They're not just charities—nonprofits include universities, hospitals, advocacy groups, political organizations, PTAs, and even [professional football teams](https://en.wikipedia.org/wiki/Green_Bay_Packers,_Inc.)!

This class is designed to build your awareness of the role and importance of the nonprofit sector and better prepare you to be a nonprofit and public sector leaders and a better citizen.

By the end of the course, you'll be able to:

- **Discover** a deeper appreciation for the nonprofit sector and its size, diversity, and importance in American society
- **Distinguish** between public, private, and nonprofit organizations and **identify** the core purposes of a nonprofit organization
- **Understand** the special legal structure and financial status of nonprofit organizations
- **Create** a hypothetical nonprofit organization that is focused on a particular social issue, complete with a mission statement, organizational structure, budget, fundraising strategy, marketing plan, and diversity strategy
- **Collaborate** effectively and professionally in a team


## Course materials

There is one official textbook for the class:

- Gary M. Grobman, *An Introduction to the Nonprofit Sector: A Practical Approach for the Twenty-First Century,* 6th ed. (Harrisburg, Pennsylvania: White Hat Communications, 2021). (**<span>$45</span> new at [Amazon](https://www.amazon.com/Introduction-Nonprofit-Sector-Practical-Twenty-First/dp/1929109865/)**)

We'll be using the 6th edition, but the 5th edition should still mostly work (there's a new chapter 13 in the 6th edition that messes up the later chapter numbers, so that chapter 14 in the 5th edition is chapter 16 in the 6th edition, and so on). 

There will also occasionally be additional articles or videos to read and watch. When this happens, links to these other resources will be included on the class page for that week.


## Attendance and participation

You're expected to come to class each Thursday prepared, having (1) read the material and (2) completed the pre-class check-in on iCollege.

Attendance and participation are important to your success in this course. However, we're in the middle of a deadly global pandemic and *so many people* are getting sick. If you are sick or are incapable of participating meaningfully in class (e.g. you have stayed up all night and are going to fall asleep in class), please stay home.

I will (kind of) track attendance through the pre-class check-ins (more on those in the [assignments section](/assignment/pre-class-check-in.qmd)). You'll earn 0.5 points for being in class. That's a tiny amount, and it's a fraction so it's easy for me to see it in the gradebook. If you have to miss class, there's very little penalty.

**The official attendance policy for the class is thus "please try to attend," and the official participation policy is "please try to participate."**

GSU has some new process for getting absences excused because of illness, but I don't care about that process. If you're sick, I don't need a doctor's note or anything. If a relative dies and you have to attend a funeral, do it!—don't worry about sending me confirmation or anything. If you have kids and your childcare situation falls through one week, focus on your kids!—again, don't worry about sending me confirmation. You're all adults—I trust you.

If you test positive for COVID-19, report it at <https://cc-gsu.force.com/s/>, hunker down, and focus on getting better! Please do not come to class. 

You will be working in a team throughout the semester, so make sure you coordinate with your teammates when sickness strikes. 


## Pandemic stuff

### Masks and vaccines

<small>GSU does not require this and I can't require this but I am allowed to urge it so here's me urging it:</small><br>Please get the COVID-19 vaccination and a booster shot ([sign up for one here!](https://covidinfo.gsu.edu/covid-19-resources/covid-19-vaccine/)). It is free. It saves lives. (I am fully vaccinated and boosted.)

GSU and the University System of Georgia do not have a mask mandate for students or faculty. However, I personally will be wearing a mask when [the CDC's community transmission levels](https://covid.cdc.gov/covid-data-tracker/#county-view?list_select_state=Georgia&data-type=Risk&list_select_county=13121) in the Atlanta area are medium or above.

**I strongly recommend/urge/encourage you to wear a mask in class on Mondays** regardless of your vaccination status. I will place a box of disposable masks by the door if you would like one. 

Again, GSU does not require either vaccines or masks, and if you aren't vaccinated or don't wear a mask, there are no penalties.

### Learning during a pandemic

Life absolutely sucks right now. None of us is really okay. **We're all just pretending.**

You most likely know people who have lost their jobs, have tested positive for COVID-19, have been hospitalized, or have even died (I myself know people in all those categories). You all have increased (or possibly decreased) work responsibilities and increased family care responsibilities—you might be caring for extra people (young and/or old!) right now, and you are likely facing uncertain job prospects (or have been laid off!).

**I'm fully committed to making sure that you learn everything you were hoping to learn from this class!** I will make whatever accommodations I can to help you finish your problem sets, do well on your projects, and learn and understand the class material. Under ordinary conditions, I am flexible and lenient with grading and course expectations when students face difficult challenges. Under pandemic conditions, that flexibility and leniency is intensified.

If you tell me you're having trouble, I will not judge you or think less of you. I hope you'll extend me the same grace.

You *never* owe me personal information about your health (mental or physical). You are *always* welcome to talk to me about things that you're going through, though. If I can't help you, I usually know somebody who can.

If you need extra help, or if you need more time with something, or if you feel like you're behind or not understanding everything, **do not suffer in silence!** Talk to me! I will work with you. **I promise.**

*Please* sign up for a time to meet with me during student hours at <https://calendly.com/andrewheiss/>. I'm also available through e-mail.

I want you to learn lots of things from this class, but I primarily want you to stay healthy, balanced, and grounded during this crisis.


## Course policies

**Be nice. Be honest. Don't cheat.**

We will also follow [Georgia State's Code of Conduct](https://codeofconduct.gsu.edu/).

This syllabus reflects a plan for the semester. Deviations may become necessary as the semester progresses.

### Student hours

Please watch this video:

<iframe src="https://player.vimeo.com/video/270014784" width="640" height="360" frameborder="0" allow="autoplay; fullscreen" allowfullscreen style="display: block; margin: 0 auto 1rem;"></iframe>

Student hours are set times dedicated to all of you (most professors call these "office hours"; I don't^[There's fairly widespread misunderstanding about what office hours actually are! [Many students often think that they are the times I *shouldn't* be disturbed](https://www.chronicle.com/article/Can-This-Man-Change-How-Elite/245714/), which is the exact opposite of what they're for!]). This means that I will be ~~in my office~~ at home (wistfully) waiting for you to ~~come by~~ talk to me remotely with whatever questions you have. This is the best and easiest way to find me and the best chance for discussing class material and concerns.

Because of the pandemic, it is easiest to meet with me online via Webex for student hours. [Make an appointment with me here](https://calendly.com/andrewheiss/), and then use this link to talk to me during student hours: <https://gsumeetings.webex.com/meet/aheiss>. You can also find me through e-mail.

### Late work

You will lose 1 point per day for each day a problem set is late. This is designed to not be a huge penalty (3 days late = 27/30 points on a problem set that gets a ✓), but instead is a commitment device to help you stay on schedule.

### Counseling and Psychological Services (CPS)

Life at GSU can be complicated and challenging (especially during a pandemic!). You might feel overwhelmed, experience anxiety or depression, or struggle with relationships or family responsibilities. [Counseling and Psychological Services (CPS)](https://education.gsu.edu/cps/) provides free, *confidential* support for students who are struggling with mental health and emotional challenges. The CPS office is staffed by professional psychologists who are attuned to the needs of all types of college and professional students. Please do not hesitate to contact CPS for assistance—getting help is a smart and courageous thing to do.

### Basic needs security

If you have difficulty affording groceries or accessing sufficient food to eat every day, or if you lack a safe and stable place to live, and you believe this may affect your performance in this course, please contact the [Dean of Students](https://deanofstudents.gsu.edu/) for support. They can provide a host of services including free groceries from the [Panther Pantry](https://nutrition.gsu.edu/panther-pantry/) and assisting with homelessness with the [Embark Network](https://deanofstudents.gsu.edu/student-assistance/embark/). Additionally, please talk to me if you are comfortable in doing so. This will enable me to provide any resources that I might possess.

### Lauren's Promise

**I will listen and believe you if someone is threatening you.**

Lauren McCluskey, a 21-year-old honors student athlete, [was murdered on October 22, 2018 by a man she briefly dated on the University of Utah campus](https://www.sltrib.com/opinion/commentary/2019/02/10/commentary-failing-lauren/). We must all take action to ensure that this never happens again.

If you are in immediate danger, call 911 or GSU police (404-413-3333).

If you are experiencing sexual assault, domestic violence, or stalking, please report it to me and I will connect you to resources or call [GSU's Counseling and Psychological Services](https://counselingcenter.gsu.edu/crisis-services/concern-self/immediate-help/) (404-413-1640).

Any form of sexual harassment or violence will not be excused or tolerated at Georgia State. GSU has instituted procedures to respond to violations of these laws and standards, programs aimed at the prevention of such conduct, and intervention on behalf of the victims. Georgia State University Police officers will treat victims of sexual assault, domestic violence, and stalking with respect and dignity. Advocates on campus and in the community can help with victims' physical and emotional health, reporting options, and academic concerns.

### Academic honesty

Violation of [GSU's Policy on Academic Honesty](https://deanofstudents.gsu.edu/faculty-staff-resources/academic-honesty/) will result in an F in the course and possible disciplinary action.^[So seriously, just don't cheat or plagiarize!] All violations will be formally reported to the Dean of Students.

### Special needs

Students who wish to request accommodation for a disability may do so by registering with the [Office of Disability Services](https://disability.gsu.edu/). Students may only be accommodated upon issuance by the Office of Disability Services of a signed [Accommodation Plan](https://disability.gsu.edu/services/how-to-register/) and are responsible for providing a copy of that plan to instructors of all classes in which accommodations are sought.

Students with special needs should then make an appointment with me during the first week of class to discuss any accommodations that need to be made.


## Assignments and grades

You can find descriptions for all the assignments on the [assignments page](/assignment/).

```{r assignments-grades, include=FALSE}
assignments <- tribble(
  ~Points,   ~Assignment,
  12 * 16.5, "Pre-class check-ins (12 × 16.5)",
  40,        "Why nonprofits?",
  30,        "Team charter",
  40,        "Community, issue, mission, and vision",
  50,        "Organizational structure",
  50,        "Revenue plan and budget",
  50,        "Fundraising and marketing",
  40,        "Diversity strategy",
  150,       "Final presentation",
  150,       "Final portfolio",
  2,         "Two free points to make a nice denominator"
) %>%
  mutate(Percent = Points / sum(Points),
         Percent = scales::percent(Percent))

grading <- tribble(
  ~Grade, ~Range, ~Grade1, ~Range1,
  "A",  "93–100%", "C",  "73–76%",
  "A−", "90–92%", "C−", "70–72%",
  "B+", "87–89%", "D+", "67–69%",
  "B",  "83–86%", "D",  "63–66%",
  "B−", "80–82%", "D−", "60–62%",
  "C+", "77–79%", "F",  "< 60%"
)
```

<div class="centered-table">

```{r show-assignments-table, echo=FALSE, results="asis"}
assignments_total <- tibble(Assignment = "Total",
                            Points = sum(assignments$Points),
                            Percent = NA)

bind_rows(assignments, assignments_total) %>%
  select(Assignment, Points, Percent) %>%
  pandoc.table(justify = "lcc", missing = "—")
```
</div>

<div class="centered-table">

```{r show-grades-table, echo=FALSE, results="asis"}
grading %>%
  pandoc.table(justify = "lclc",
               col.names = c("Grade", "Range", "Grade", "Range"))
```

<div>


## Comic books

Once you have read this entire syllabus and [the assignments page](/assignment/), please [click here](mailto:aheiss@gsu.edu) and e-mail me a picture of your favorite comic book character.
