---
title: "Ethics"
author: "Andrew Heiss"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: "libs"
    chakra: "libs/remark-latest.min.js"
    css: ["default", "css/ath-slides.css", "css/ath-jost-fonts.css", "css/animate.css"]
    seal: false
    anchor_sections: false
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
      ratio: "16:9"
      navigation:
        scroll: false
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
                      fig.retina = 3, fig.align = "center")
```

```{r packages-data, include=FALSE}
library(countdown)
```

```{r xaringanExtra, echo=FALSE}
xaringanExtra::use_xaringan_extra(c("tile_view"))
```

class: center middle main-title section-title-2

# Ethics

.class-info[

**November 10, 2022**

.light[PMAP 3210: Introduction to Nonprofits<br>
Andrew Young School of Policy Studies
]

]

---

name: outline
class: title title-inv-5

# Plan for today

--

.box-2.medium.sp-after[Ethics in the nonprofit sector]

--

.box-6.medium.sp-after[Ethical frameworks]

--

.box-3.medium[An ethics toolkit]

---

layout: false
name: nonprofits
class: center middle section-title section-title-2 animated fadeIn

# Ethics in the<br>nonprofit sector

---

layout: true
class: title title-2

---

# What is ethics?

--

> “…well-founded standards of right and wrong that prescribe what humans ought to do, usually in terms of rights, obligations, benefits to society, fairness, or specific virtues…”

--

.box-2.medium[How to decide the "right" thing to do]

???

<https://www.scu.edu/ethics/ethics-resources/ethical-decision-making/what-is-ethics/>

---

# General types of ethical problems

--

.pull-left[
.box-inv-2[Managerial mischief]

.box-2[Behavior that reasonable people would clearly recognize as being wrong]
]

--

.pull-right[
.box-inv-2[Moral mazes]

.box-2[Less wrongful behavior that managers deal with on a daily basis]
]

---

# General types of ethical problems

--

.pull-left[
.box-inv-2[Managerial mischief]

.box-2.small[Covering up harmful mistakes to protect the organization]

.box-2.small[Diverting nonprofit funds for personal use]

.box-2.small[Misleaading donors on how funds will be spent]
]

--

.pull-right[
.box-inv-2[Moral mazes]

.box-2.small[Using nonprofit office supplies for personal things]

.box-2.small[Conscious use of nonprofit funds in an inefficient manner]

.box-2.small[Contracting to a relative of a board member]
]

---

# Nonprofit ethical accountability

.box-inv-2[Nonprofits have a legal and ethical responsibility to:]

--

.box-2[Donors]

--

.box-2[Clients]

--

.box-2[Board and staff]

--

.box-2[General public]

---

# Ethical accountability

.box-inv-2[Nonprofits should care about<br>these aspects of accountability:]

--

.box-2[How they govern their organization]

--

.box-2[How they spend their money]

--

.box-2[The truthfulness of nonprofit representations]

--

.box-2[Their willingness to disclose basic information to the public]

---

# Creating ethical nonprofits

--

.box-inv-2[Codes of ethics]

.center.smaller[[The Mott Foundation's code of ethics](https://www.mott.org/about/values/)]

--

.box-inv-2[Ethics trainings]

.center.smaller[[Merit Leadership](https://meritleadership.com/)]

--

.box-inv-2[Ethics hotlines]

.center.smaller[[CARE's EthicsPoint hotline](https://secure.ethicspoint.eu/domain/media/en/gui/100612/index.html)]

--

.box-inv-2[Organizational culture]

???

<https://www.councilofnonprofits.org/tools-resources/code-of-ethics-nonprofits-why-your-nonprofit-may-want-adopt-statement-of-values>

---

layout: false
name: frameworks
class: center middle section-title section-title-6 animated fadeIn

# Ethical frameworks

---

class: middle

> I’ve just been sent a baby present from a key supplier. It’s a small gift, a sign of goodwill thanks to work I’ve done to improve an unstable relationship between our companies. My organization forbids employees from accepting gifts of any kind from suppliers, but I also know that my boss accepted a similar gift just two weeks ago. If I keep the gift, nobody will know, but if I send it back, I’ll probably hurt someone’s feelings.

---

layout: true
class: title title-6

---

# Why use ethical frameworks?

--

.box-inv-6.medium[There is never one right answer<br>to an ethical problem]

--

.box-inv-6.medium[There are different ways<br>of thinking about problems]

---

# My favorite four frameworks

--

.pull-left[
.box-inv-6[**Teleology /<br>utilitarianism**<br>.smaller[Focus on the outcomes and ends]]

.box-inv-6[**Deontology**<br>.smaller[Focus on the means and universal rules]]
]

--

.pull-right[
.box-inv-6[**Virtue ethics**<br>.smaller[Make best possible version of yourself]]

.box-inv-6[**Moral contractualism /<br>decency**<br>.smaller[Make best possible version of others]]
]

???

- Utilitarianism/teleology - good ends
- Deontology - good, universal means
- Virtue ethics - making the best possible version of yourself
- Empathy and decency - making the best possible version of others

---

# Teleology / Utilitarianism

--

.pull-left[
.box-inv-6[Teleology]

.box-6.SMALL[Decisions should be based on *results*; results should create most good and least evil]

.box-6.SMALL["The ends justify the means"]
]

--

.pull-right[
.box-inv-6[Utilitarianism]

.box-6.SMALL[Decisions should be based on<br>*the greatest good<br>for the most people*]

.box-6.SMALL[Literal moral calculus using<br>"utils," or happiness points]
]

---

# Teleology / Utilitarianism

.center[
<iframe width="889" height="500" src="https://www.youtube.com/embed/YuVreCbQOwc" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
]

---

# Deontology

--

.pull-left[
.box-inv-6[Immanuel Kant's<br>categorical imperative]

> Act only according to that maxim whereby you can, at the same time, will that it should become a universal law.
]

--

.pull-right[
.box-inv-6.SMALL[Decisions should be based on *whether they are the right thing to do,* regardless of consequences. The circumstance shouldn't matter]

.box-inv-6.SMALL[All actions should be universalizable—what I do, anybody else can do]
]

---

# Deontology

.center[
<iframe width="889" height="500" src="https://www.youtube.com/embed/2S_XuJTOEJY" frameborder="0" allow="accelerometer; autoplay; encrypted-media; gyroscope; picture-in-picture" allowfullscreen></iframe>
]

---

# Virtue ethics

--

.box-inv-6.SMALL[Decisions should be made by people with<br>*benevolence* who possess specific virtues]

--

.pull-left[
.box-inv-6.small[Aristotle's cardinal virtues:]

.box-6.smaller[Fortitude (courage)]

.box-6.smaller[Temperance (moderation)]

.box-6.smaller[Prudence (wisdom)]

.box-6.smaller[Justice]
]

--

.pull-right[
.box-inv-6.small[Universal-ish virtues:]

.box-6.smaller[Honesty]

.box-6.smaller[Responsibility]

.box-6.smaller[Respect]

.box-6.smaller[Fairness]

.box-6.smaller[Compassion]
]

---

# Moral contractualism & decency

--

.pull-left[
.box-6[**We owe things<br>to each other.**]

.box-inv-6.small[We should design rules that can't be rejected by the people we share the world with.]

.box-inv-6.smaller[T. M. Scanlon's *What We Owe To Each Other* (2000) and Todd May's *A Decent Life* (2019)]
]

--

.pull-right[
.box-inv-6[Decisions should reduce human suffering and lift others up]

.box-inv-6[Human relationships are central—what decision best enables and enhances our social contract?]
]

???

<https://www.vox.com/future-perfect/2019/9/26/20874217/the-good-place-series-finale-season-4-moral-philosophy>

<https://godplaysdice.com/2019/11/05/book-review-a-decent-life-by-todd-may/>

<https://godplaysdice.com/2018/05/30/who-is-my-neighbor/>

Todd May and The Good Place

---

layout: false
class: middle

.box-inv-6.medium[You find $50 on the floor after class.<br>Do you track down the person<br>it might belong to, or keep it?]

---

layout: true
class: title title-6

---

# Teleological / utilitarian logic

--

.box-inv-6.less-medium[Maximize happiness and minimize pain<br>by analyzing consequences]

--

.box-inv-6.small[Getting more money gives you more utility, but it is offset by guilt]

--

.box-inv-6.small[Consequences: get richer, get caught, feel happy, feel sad, person who lost the money really needed it, you really needed it, waste time finding person]

--

.box-6.small[Stick all that information into a magic formula in your head.<br>If keeping it gives you the most utility, keep it. Otherwise don't.]

---

# Teleological / utilitarian logic

--

.box-inv-6.less-medium[Achieves the "greatest good for<br>the greatest number"]

--

.box-inv-6.less-medium[Foundation for public policy]

--

.box-6[BUT! As long as the outcome is good,<br>it doesn't matter how you get there.]

---

# Deontological / Kantian logic

--

.box-inv-6.less.medium[No need for moral calculus.<br>Give the money back.]

--

.box-inv-6["What I do, anybody else can do"]

--

.box-inv-6[If everyone kept money they found,<br>the world would be worse off]

--

.box-inv-6[Finding the original owner could be a universal law]

---

# Deontological / Kantian logic

--

.box-inv-6.less-medium[The rules and process matter]

--

.box-inv-6[BUT pure Kantians don't allow for exceptions<br>(and thus don't really exist IRL)]

--

.box-inv-6.smaller[You can't lie to a murderer at the door because lying cannot be universalized]

---

# Virtue ethics logic

--

.box-inv-6.less-medium[An action is good if it<br>maintains integrity and builds character]

--

.box-6[Pretty much every agreed-upon virtue<br>(honesty, responsibility, respect, fairness, compassion, etc.)<br>says to give the money back]

---

# Virtue ethics logic

--

.box-inv-6.less-medium[Virtue ethics isn't very normative or universal]

&nbsp;

--

.box-inv-6[Quick way to test virtues is the *disclosure rule*:]

--

.box-6.less-medium[How would you feel if your<br>response appeared in the media?]

---

# Moral contractualism.smaller[&nbsp;& ]decency logic

--

.box-inv-6.less-medium[**We owe things to each other.**]

--

.box-inv-6[Our decision should reduce<br>human suffering and lift others up]

--

.box-inv-6.SMALL[Consider why the $50 is there. Someone who was planning to<br>use it for something useful probably dropped it on accident.<br>Reduce suffering by finding them.]

--

.box-6[We have a social obligation to do this.]

---

layout: false
name: toolkit
class: center middle section-title section-title-3 animated fadeIn

# An ethics toolkit

---

layout: true
class: title title-3

---

# The Ethics Toolkit

.pull-left.color-7[
- **Gather the facts**
- **Define the ethical issues**
- **Identify the affected parties**
]

.pull-right.SMALL.color-7[
- **Identify the consequences** .small[(utilitarianism)]
- **Identify the obligations** .small[(deontology)]
- **Consider your character and integrity** .small[(virtue ethics)]
- **Consider what would be decent and most helpful for others** .small[(moral contractualism)]
]

---

layout: false
class: middle

> I’ve just been sent a baby present from a key supplier. It’s a small gift, a sign of goodwill thanks to work I’ve done to improve an unstable relationship between our companies. My organization forbids employees from accepting gifts of any kind from suppliers, but I also know that my boss accepted a similar gift just two weeks ago. If I keep the gift, nobody will know, but if I send it back, I’ll probably hurt someone’s feelings.

---

.pull-left[
.box-inv-3[**Teleology /<br>utilitarianism**<br>.smaller[Focus on the outcomes and ends]<br>]

.center.smaller[(Words like "results", "outcomes",<br>"effect", "consequences")]<br>

.box-inv-3[**Deontology**<br>.smaller[Focus on the means and universal rules]]

.center.smaller[(Words like "rights", "justice",<br>"fairness", "rules")]
]

.pull-right[
.box-inv-3[**Virtue ethics**<br>.smaller[Make best possible version of yourself]]

.center.smaller[(Words like "character",<br>"integrity", "reputation")]<br>

.box-inv-3[**Moral contractualism /<br>decency**<br>.smaller[Make best possible version of others]]

.center.smaller[(Words like "obligations",<br>"expectations", "society")]
]

---

layout: true
class: middle

---

> Your organization is receiving a large donation to support research. Though you are not sure, there are some indications that the family who is providing the donation received their money through smuggling drugs. They may also be involved in money laundering.

---

> Your organization runs community health clinics in rural Haiti. To stay caught up with relevant research and to network with potential donors and volunteers, your staff attends annual conferences at expensive Swiss chalets. Is this ethical?

---

> Your organization received too much money for a program that's already well-funded. Should you divert the money to a different under-funded program?
