---
title: "Course overview and defining the nonprofit sector"
date: "2022-08-25"
---

```{r slides, echo=FALSE, include=FALSE}
source(here::here("R", "slide-things.R"))

slide_details <- tibble::tribble(
  ~title, ~slide, ~active,
  "Introduction", "1", TRUE,
  "What are nonprofits?", "what-are-nonprofits", FALSE,
  "Why do we have a class just for nonprofits?", "why-focus", FALSE,
  "What are we doing this semester?", "class-overview", FALSE
)
```

## Readings

- The [syllabus](/syllabus.qmd), [class](/class/index.qmd), and [assignments](/assignment/index.qmd) pages for this class
- {{< fa book >}} Chapter 1 in Grobman, *An Introduction to the Nonprofit Sector* [@Grobman:2021]
- {{< fa video >}} Dan Pallotta, ["The way we think about charity is dead wrong"](https://www.ted.com/talks/dan_pallotta_the_way_we_think_about_charity_is_dead_wrong?language=en)


## Slides

The slides for today's class are available online as an HTML file. Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the slides below and navigate through them with your left and right arrow keys.

```{r show-slide-tabs, echo=FALSE, results="asis"}
slide_buttons("/slides/01-slides")
slide_tabs(slide_details, "/slides/01-slides.html")
```

:::{.callout-tip}
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::
