---
title: "History and theory of the nonprofit sector"
date: "2022-09-01"
---

```{r slides, echo=FALSE, include=FALSE}
source(here::here("R", "slide-things.R"))

slide_details <- tibble::tribble(
  ~title, ~slide, ~active,
  "Introduction", "1", TRUE,
  "Theory", "theory", FALSE,
  "History", "history", FALSE,
  "How to make teamwork not suck", "teams-not-suck", FALSE
)
```

## Readings

- {{< fa book >}} Chapters 2 and 3 in Grobman, *An Introduction to the Nonprofit Sector* [@Grobman:2021]
- {{< fa file-pdf >}} Monash University Engineering Department, ["Learning effectively through groupwork"](https://www.monash.edu/__data/assets/pdf_file/0004/506434/groupwork.pdf)
- {{< fa arrow-up-right-from-square >}} University of Waterloo's Centre for Teaching Excellence, ["Teamwork Skills: Being an Effective Group Member"](https://uwaterloo.ca/centre-for-teaching-excellence/teaching-resources/teaching-tips/tips-students/being-part-team/teamwork-skills-being-effective-group-member)
- {{< fa arrow-up-right-from-square >}} Jayson Demers, ["8 Teamwork Tips for Working with Unfamiliar Co-Workers"](https://www.inc.com/jayson-demers/8-teamwork-tips-for-working-with-unfamiliar-coworkers.html)


## Written response question

Explore this question in ≈150 words, based on your readings for today: 

> Do you think that the growth of federal spending for the welfare state in the mid-20th century (for instance, under Lyndon B. Johnson’s War on Poverty) stimulated or hindered the growth of the nonprofit sector in the United States? What other social consequences have there been as a result of turning to nonprofits for welfare services?


## Team prep work

Last week, I asked you to tell me what kind of social issue or type of nonprofit you’d be most interested in. In preparation for today’s team work, you’ll need to expand on that.

Think of a social issue or cause that you’d be interested in creating a nonprofit for. In ≈150 words, justify why (or why not) the issue should be addressed by the nonprofit sector. What kind of public goods would it provide? Why doesn’t the government or the private sector do it instead? (Think of the theory readings). Which IRS category would it fall under?


## Example charters

Your first team assignment is to create a charter ([see the instructions here](/assignment/00-team-charter.qmd)).

These are ***by no means*** ideal or perfect or anything. One is an ultra generic template; two are charters I dug up from my time as an MPA (master of public administration) student. But they'll give you a good feel for what should be in a charter.

- {{< fa file-pdf >}} [Team charter example](https://international.humber.ca/assets/files/Group-or-Team-Charter.pdf) from the International Centre at Humber College 
- {{< fa file-pdf >}} [Charter from Team RRRAM](/files/rrram-charter.pdf), BYU MPA Fall 2010
- {{< fa file-pdf >}} [Charter from Team Gubernator](/files/gubernator-charter.pdf), BYU MPA Winter 2011


## Slides

The slides for today's class are available online as an HTML file. Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the slides below and navigate through them with your left and right arrow keys.

```{r show-slide-tabs, echo=FALSE, results="asis"}
slide_buttons("/slides/02-slides")
slide_tabs(slide_details, "/slides/02-slides.html")
```

:::{.callout-tip}
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::
