---
title: "Regulatory issues"
date: "2022-09-15"
---

```{r slides, echo=FALSE, include=FALSE}
source(here::here("R", "slide-things.R"))

slide_details <- tibble::tribble(
  ~title, ~slide, ~active,
  "Introduction", "1", TRUE,
  "Incorporation issues", "incorporation", FALSE,
  "Money issues", "money", FALSE
)
```

## Readings

- {{< fa book >}} Chapter 4 in Grobman, *An Introduction to the Nonprofit Sector* [@Grobman:2021]
- {{< fa file-pdf >}} Chapter 1 in W. Jeffrey Garson, Donald W. Kramer, and Roberta M. Snow, *Nonprofit Leadership & the Law* [@GarsonKramerSnow:2000] (the PDF for this is on iCollege under "Content".)


## Written response question

Why did Congress prohibit tax-exempt charities from engaging in partisan political activity? Are there reasons to think that this prohibition is unwise in every case? Why did Congress prohibit "substantial lobbying" rather than all lobbying? Why is some amount of nonprofit political lobbying okay? (Answer in ≈150 words.)


## Team prep work

Write a statement arguing for or against whether your team's nonprofit should be incorporated, have membership, and apply for tax-exempt status. You'll spend class time coming to a consensus about incorporation and membership. (Answer in ≈75 words.)


## Slides

The slides for today's class are available online as an HTML file. Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the slides below and navigate through them with your left and right arrow keys.

```{r show-slide-tabs, echo=FALSE, results="asis"}
slide_buttons("/slides/04-slides")
slide_tabs(slide_details, "/slides/04-slides.html")
```

:::{.callout-tip}
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::
