---
title: "Board governance"
date: "2022-09-22"
---

```{r slides, echo=FALSE, include=FALSE}
source(here::here("R", "slide-things.R"))

slide_details <- tibble::tribble(
  ~title, ~slide, ~active,
  "Introduction", "1", TRUE,
  "What do boards do?", "boards-do", FALSE,
  "What makes a good board?", "good-boards", FALSE
)
```

## Readings

- {{< fa book >}} Chapter 5 in Grobman, *An Introduction to the Nonprofit Sector* [@Grobman:2021]
- {{< fa file-pdf >}} Barbara E. Taylor, Richard P. Chait, and Thomas P. Holland, "The New Work of the Nonprofit Board" [@TaylorChaitHolland:1996] (you can [read this online here](https://hbr.org/1996/09/the-new-work-of-the-nonprofit-board); if you run into access issues, there's a PDF of the article on iCollege under "Content". *Do not buy this article—you can read it for free*)
- {{< fa file-pdf >}} Robert D. Herman and David O. Renz, "Board Practices of Especially Effective and Less Effective Local Nonprofit Organizations" [@HermanRenz:2000] (the PDF for this is on iCollege under "Content".)

This is a helpful checklist that you'll want to review when working on your project. I'd recommend skimming it before class, but you don't need to read it in detail:

- {{< fa file-pdf >}} Chapter 4 in Peri H. Pakroo, *Starting & Building a Nonprofit* [@Pakroo:2021] (the PDF for this is on iCollege under "Content".)


## Written response question

You just read a bunch of research about what makes nonprofit boards effective. Make a list of the five practices that you find the most important and explain why nonprofits should implement them. (Answer in ≈150 words.)


## Team prep work

What type of board would be appropriate for your team's nonprofit? Why is it the best fit with your type of nonprofit? You'll spend class time deciding on the type and structure of your team's nonprofit. (Answer in ≈75 words.)


## Slides

The slides for today's class are available online as an HTML file. Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the slides below and navigate through them with your left and right arrow keys.

```{r show-slide-tabs, echo=FALSE, results="asis"}
slide_buttons("/slides/05-slides")
slide_tabs(slide_details, "/slides/05-slides.html")
```

:::{.callout-tip}
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::
