---
title: "Budgeting and financial management"
date: "2022-10-13"
---

```{r slides, echo=FALSE, include=FALSE}
source(here::here("R", "slide-things.R"))

slide_details <- tibble::tribble(
  ~title, ~slide, ~active,
  "Introduction", "1", TRUE,
  "Anatomy of a budget", "anatomy", FALSE,
  "Financial analysis", "analysis", FALSE
)
```

## Readings

- {{< fa book >}} Chapter 11 in Grobman, *An Introduction to the Nonprofit Sector* [@Grobman:2021]
- {{< fa file-pdf >}} Chapter 3 in Peri H. Pakroo, *Starting & Building a Nonprofit* [@Pakroo:2021] (the PDF for this is on iCollege under "Content".)


## Written response question

What control should the board have over the ability of nonprofit executives to spend funds to accomplish organizational objectives? Should nonprofit executives have flexibility to adjust their budgets in response to new conditions without obtaining board approval? (Answer in ≈150 words.)


## Team prep work

Put together a basic, preliminary, balanced budget for your nonprofit to propose to your team. You'll spend class time creating and finalizing your organization's budget.


## In-class materials

Spreadsheets:

- {{< fa table >}} [Example budget](https://docs.google.com/spreadsheets/d/1JB4q04jA4yO8qP6r25uVtI2O4_QpXkg-7V4xIcg1rYo/edit)
- {{< fa table >}} [990 analysis form](https://docs.google.com/spreadsheets/d/1gq0A192FNgFA9V6Z5jO8U_NhgAu9nBvJ41TZQr6aiUg/edit)

990s:

- {{< fa file-pdf >}} [CARE 2018 990](/files/990s/CARE-2018-990.pdf)
- {{< fa file-pdf >}} [CARE 2019 990](/files/990s/CARE-2019-990.pdf)
- {{< fa file-pdf >}} [CARE 2020 990](/files/990s/CARE-2020-990.pdf)
- {{< fa file-pdf >}} [Georgia Aquarium 2017 990](/files/990s/Georgia-Aquarium-2017-990.pdf)
- {{< fa file-pdf >}} [Georgia Aquarium 2018 990](/files/990s/Georgia-Aquarium-2018-990.pdf)
- {{< fa file-pdf >}} [Georgia Aquarium 2019 990](/files/990s/Georgia-Aquarium-2019-990.pdf)
- {{< fa file-pdf >}} [Center for Puppetry Arts 2018 990](/files/990s/Center-for-Puppetry-Arts-2018-990.pdf)
- {{< fa file-pdf >}} [Center for Puppetry Arts 2019 990](/files/990s/Center-for-Puppetry-Arts-2019-990.pdf)
- {{< fa file-pdf >}} [Center for Puppetry Arts 2020 990](/files/990s/Center-for-Puppetry-Arts-2020-990.pdf)
- {{< fa file-pdf >}} [Live Thrive 2017 990](/files/990s/Live-Thrive-2017-990.pdf)
- {{< fa file-pdf >}} [Live Thrive 2018 990](/files/990s/Live-Thrive-2018-990.pdf)
- {{< fa file-pdf >}} [Live Thrive 2019 990](/files/990s/Live-Thrive-2019-990.pdf)
- {{< fa file-pdf >}} [Trees Atlanta 2018 990](/files/990s/Trees-Atlanta-2018-990.pdf)
- {{< fa file-pdf >}} [Trees Atlanta 2019 990](/files/990s/Trees-Atlanta-2019-990.pdf)
- {{< fa file-pdf >}} [Trees Atlanta 2020 990](/files/990s/Trees-Atlanta-2020-990.pdf) 


## Slides

The slides for today's class are available online as an HTML file. Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the slides below and navigate through them with your left and right arrow keys.

```{r show-slide-tabs, echo=FALSE, results="asis"}
slide_buttons("/slides/08-slides")
slide_tabs(slide_details, "/slides/08-slides.html")
```

:::{.callout-tip}
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::
