---
title: "Ethics"
date: "2022-11-10"
---

```{r slides, echo=FALSE, include=FALSE}
source(here::here("R", "slide-things.R"))

slide_details <- tibble::tribble(
  ~title, ~slide, ~active,
  "Introduction", "1", TRUE,
  "Ethics in the nonprofit sector", "nonprofits", FALSE,
  "Ethical frameworks", "frameworks", FALSE,
  "An ethics toolkit", "toolkit", FALSE
)
```

## Readings

- {{< fa book >}} Chapter 7 in Grobman, *An Introduction to the Nonprofit Sector* [@Grobman:2021]
- {{< fa tv >}} "The Trolley Problem", *The Good Place* Season 2, Episode 5 (available on Netflix)


## Written response question

Should the nonprofit sector be held to a higher ethical standard than its for-profit counterpart? Why or why not? What about compared with the government sector? (Answer in ≈150 words.)


## Slides

The slides for today's class are available online as an HTML file. Use the buttons below to open the slides either as an interactive website or as a static PDF (for printing or storing for later). You can also click in the slides below and navigate through them with your left and right arrow keys.

```{r show-slide-tabs, echo=FALSE, results="asis"}
slide_buttons("/slides/12-slides")
slide_tabs(slide_details, "/slides/12-slides.html")
```

:::{.callout-tip}
**Fun fact**: If you type <kbd>?</kbd> (or <kbd>shift</kbd> + <kbd>/</kbd>) while going through the slides, you can see a list of special slide-specific commands.
:::

